Title here

### 2016-12-06 portfolio/text/ms.Rmd
Revert "weird sync issue"
This reverts commit be32164a98a0818fc1cbb2b83070a1ef78a97abe.

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(cache=TRUE, echo=FALSE, message=FALSE, autodep=TRUE,
  results='hide')
opts_chunk$set(warning=FALSE, message=FALSE, cache.path="../cache/",
  cache.lazy=TRUE)
```
```{r get-dat, cache=FALSE}
load("../data-generated/output-values.rda")
h1 <- readRDS("../data-generated/h1_effect.rds")
spoke <- readRDS("../data-generated/spoke_fraction.rds")
g2_dens <- readRDS("../data-generated/g2_prob_dens_above_zero.rds")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
```

@@

Using a unique dataset collected over 30 years (1985--2014) on individuals,
rather than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals rather than
vessels we can track people that switch fishery sectors over time, or alter
strategies and use multiple vessels. We develop and apply a hierarchical
Bayesian model to understand the effect of diversity on both individual revenue
and revenue variability that builds on results from vessel [@kasperski2013],
fleet [@sethi2012b], and community-level variability [@sethi2014]. Our model
controls for fishing effort and latent time effects (e.g. changing environmental
conditions), simultaneously estimates the effect of species diversity on
individual revenue and revenue variability, and estimates effects both within
and across fishing strategies (sets of similar licenses or permits). To our
knowledge, this is the first application of this type of model in any natural
resource field.

@@

We developed a hierarchical variance-function regression model, which separately
models changes in the mean and variance of individual revenue as a function of
covariates [@davidian1987; @hall1989]. Whereas traditional hierarchical linear
models assume homoscedasticity --- that the residual variance does not vary
systematically --- the variance-function regression model allows the variance to
be heteroscedastic and vary as a function of covariates. Our specific model
allows certain fishing strategies and levels of species diversification to
generate more or less revenue and be more or less variable than others.

>>>>

```{r set-knitr-options, cache=FALSE, echo=FALSE}
library("knitr")
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, results='hide')
```
```{r get-dat}
load("../data-generated/output-values.rda")
h1 <- readRDS("../data-generated/h1_effect.rds")
spoke <- readRDS("../data-generated/spoke_fraction.rds")
g2_dens <- readRDS("../data-generated/g2_prob_dens_above_zero.rds")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
```

@@

Using a unique dataset collected over 30 years (1985--2014) on individuals,
rather than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals rather than
vessels we can track people that switch fishery sectors over time, or alter
strategies and use multiple vessels. We develop and apply a hierarchical
Bayesian model to understand the effect of diversity on both individual revenue
and revenue variability that builds on results from vessel [@kasperski2013],
fleet [@sethi2012b], and community-level [@sethi2014] variability. Our model
controls for fishing effort and latent time effects (e.g. changing environmental
conditions), simultaneously estimates the effect of species diversity on
individual revenue and revenue variability, and estimates effects both within
and across fishing strategies (sets of similar licenses or permits). To our
knowledge, this is the first application of this type of model in any natural
resource field.

@@

We developed a hierarchical variance-function regression model [@davidian1987;
@hall1989], which separately models changes in the mean and variance of
individual revenue as a function of covariates. Whereas traditional
hierarchical linear models assume homoscedasticity --- that the residual
variance does not vary systematically --- the variance-function regression model
allows the variance to be heteroscedastic and vary as a function of predictors.
Our specific model allows certain fishing strategies and levels of species
diversification to generate more or less revenue and be more or less variable
than others.
